### 2021-10-12 paper/pldi22/abstract.tex
Revised abstract

\begin{abstract}\label{sec:abstract}
  \todo
\end{abstract}

>>>>

\begin{abstract}\label{sec:abstract}
  JavaScript is a widely-used programming language in various fields. Recently,
  it rapidly evolved with a yearly release cadence and open development process
  to quickly adapt users’ demands to the language. In this fast-evolving nature
  of JavaScript, the need for \textit{language design assistants} has grown to
  understand original or revised semantics in the revision process correctly.
  Unfortunately, while several tools have been proposed as language design
  assistants for JavaScript in academia and industry, they should be manually
  updated to represent revised semantics every time. Besides, they lack the
  additional information for better comprehension of language semantics,
  including the relationship between specific semantics with conformance tests.

  To alleviate this problem, we present $\tool$, a \textit{live} language design
  assistant for JavaScript. It automatically synchronizes with a given language
  specification and shows related conformance tests in the revision process.
  Moreover, to better comprehend language semantics, we present a way to focus
  on specific semantics by automatically reducing semantics and filtering out
  conformance tests with user-defined \textit{syntactic views}. In this paper,
  we conduct several case studies for JEDIT to demonstrate the effectiveness of
  live language design with syntactic views. Moreover, we experimentally show
  that syntactic views successfully reduce the \inred{XX.X}\% of semantics and
  filter out \inred{XX.X}\% of conformance tests on average using historically
  representative syntactic views.
\end{abstract}
